---
title: |
  ETC5543 Business Analytics Creative Activity 
  
  Project Report
date:  "`r format(Sys.time(), '%d %B, %Y')`"
author: |
  | Xianghe Xu
  |
  | 32929447
  |
  | [Project Github Repository Link](https://github.com/xxuu0086/ETC5543_Internship_Project) 
  
team: Group 1
subtitle: |
  Department of Econometrics and Business Statistics

  Monash University
  
  | - 
  
  __The Australian Comparative Study of Survey Method Data Quality Project.__
  
  | -
  
abstract: |
  **Purpose**: The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.

  **Methods:** The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.

  **Results:** The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.

  **Conclusion:** The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.}

# bibliography: bibliography.bib
header-includes: 
  - \renewcommand{\and}{\\ \\}
  - \AddToHook{env/abstract/before}{\vspace*{2cm}}
  - \makeatletter\AddToHook{cmd/@date/before}{\vspace*{2cm}}\makeatother
output:
  bookdown::pdf_document2:
    toc: FALSE
    number_sections: TRUE
    keep_md: yes
  html_document: default
   


---

\newpage

\newpage

[This report is for ETC5543 Business Analytics Creative Activity internship project by student __Xianghe Xu__, the github repository for this project is [https://github.com/xxuu0086/ETC5543_Internship_Project](https://github.com/xxuu0086/ETC5543_Internship_Project) .]{style="color:#006DAE;"}

\tableofcontents
\newpage

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  message = FALSE,  
  warning = FALSE,  
  error = FALSE,    
  out.width = "70%",
  fig.align = "center",
  fig.width = 8, 
  fig.height = 7,
  fig.retina = 3,
  fig.pos = "H", 
  out.extra = "",
  dev = "png")
```

```{r}
# Load packages and data
library(tidyverse)
library(haven)
library(shiny)
library(kableExtra)
library(gridExtra)
library(naniar)

dat <- haven::read_sav("../Data and survey materials/ACSSM_Merged.sav")
```

```{r}
dat1 <- dat %>% 
  mutate(prob_based = ifelse(DataSource <= 5, "Probablity based", "Non-probablity based")) %>% # Indicate probability based
  filter(DataSource %in% c(2, 5, 6, 7, 8, 9)) # Filter data source

```


```{r}
# Mutate new column with DataSource name
dat1 <- dat1 %>% 
  mutate(DataSource_name = case_when(
    DataSource == 2 ~ "Life in Australia",
    DataSource == 5 ~ "SMS push to web",
    DataSource == 6 ~ "Panel 1",
    DataSource == 7 ~ "Panel 2",
    DataSource == 8 ~ "Panel 3",
    DataSource == 9 ~ "Panel 4")) %>% 
  mutate(DataSource_name = factor(DataSource_name,
                       levels = c("Life in Australia",
                                  "SMS push to web",
                                  "Panel 1",
                                  "Panel 2",
                                  "Panel 3",
                                  "Panel 4"),
                       labels = c("Life in Australia",
                                  "SMS push to web",
                                  "Panel 1",
                                  "Panel 2",
                                  "Panel 3",
                                  "Panel 4"))) # Use str() to check levels
```

# Introduction and Motivation
(include the readings)

# Survey quality metrics

# Data Description

# Chanllenges
- Understand the metrics
- matching the metrics to variables

# Preliminary Analysis

# Analysis

# Limitation

# Summary

\newpage

# Reference

__Citation of R package__

Wickham H, Averick M, Bryan J, Chang W, McGowan LD, François R, Grolemund G, Hayes A, Henry L, Hester J, Kuhn M, Pedersen TL,
  Miller E, Bache SM, Müller K, Ooms J, Robinson D, Seidel DP, Spinu V, Takahashi K, Vaughan D, Wilke C, Woo K, Yutani H (2019).
  “Welcome to the tidyverse.” _Journal of Open Source Software_, *4*(43), 1686. doi:10.21105/joss.01686
  <https://doi.org/10.21105/joss.01686>.
  
Xie Y (2023). _bookdown: Authoring Books and Technical Documents with R Markdown_. R
  package version 0.35, <https://github.com/rstudio/bookdown>.
  
\newpage

# Appendix: All code for this report

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```
